Precise predictions for same-sign W-boson scattering at the LHC

### 2018-03-05 Draft/scanNLO.tex
small fix

These differences are much more evident in differential distributions.
In Fig.~\ref{fig:mjjdyjj_1d_1}, we show the distributions in the di-jet invariant mass $m_{\Pj\Pj}$ and rapidity separation $|\Delta y_{\Pj\Pj}|$.
For large $m_{\Pj\Pj}$ and large $|\Delta y_{\Pj\Pj}|$, as expected, the VBS approximation is performing well and its $s$-channel extension agrees with the full calculation within $10\%$ per cent.
% On the other hand, for low invariant and low rapidity separation the the VBS approximation is failing at a level of at least $30\%$.
% In this very same region, the VBS approximation with $s$-channel is good within $10\%$.
This is in contrast with the region  $200 \GeV < m_{\Pj\Pj} < 500 \GeV$ and $2<|\Delta y_{\Pj\Pj}|<2.5$, where
the difference between the $|t|^2+|u|^2$ approximation and the full computation reaches $30\%$.
The inclusion of $s$-channels cures partly this behaviour in this region.
Still, for the very low $m_{\Pj\Pj}$ a difference of about $5\%$ remains.
This tends to indicate that interference contributions and/or non-factorisable QCD corrections play a non-negligible role in this phase-space region.

>>>>

These differences are much more evident in differential distributions.
In Fig.~\ref{fig:mjjdyjj_1d_1}, we show the distributions in the di-jet invariant mass $m_{\Pj\Pj}$ and rapidity separation $|\Delta y_{\Pj\Pj}|$.
For large $m_{\Pj\Pj}$ and large $|\Delta y_{\Pj\Pj}|$, as expected, the VBS approximation is performing well and its $s$-channel extension agrees with the full calculation within $10\%$ per cent.
% On the other hand, for low invariant and low rapidity separation the the VBS approximation is failing at a level of at least $30\%$.
% In this very same region, the VBS approximation with $s$-channel is good within $10\%$.
This is in contrast with the region  $200 \GeV < m_{\Pj\Pj} < 500 \GeV$ and $2<|\Delta y_{\Pj\Pj}|<2.5$, where
the difference between the $|t|^2+|u|^2$ approximation and the full computation can reach $30\%$.
The inclusion of $s$-channels cures partly this behaviour in this region.
Still, for the very low $m_{\Pj\Pj}$ a difference of more than $10\%$ remains.
This tends to indicate that interference contributions and/or non-factorisable QCD corrections play a non-negligible role in this phase-space region.
